2-factor-Hull-White\_model\_calibration

### 2020-04-12 Submission1.tex
Added Conclusion

    \begin{center}
    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{images/output_41_0.png}
    \end{center}
    { \hspace*{\fill} \\}

\section{Conclusion}

>>>>

    \begin{center}
    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{images/output_41_0.png}
    \end{center}
    { \hspace*{\fill} \\}
\section{Conclusion}
We are well aware that Black-Scholes formula was derived under assumptions which might not hold in a real market, as an example, if the share price deviates from the geometric Brownian motion, then our estimates can be wrong by a big margin.  However with the assumptions of Black-Scholes-Merton model we were able to price a European Up-and-out Call Option.  We were able to use knowledge from module 2 and 3 to generate Python code for monthly simulations for the lifetime of the option.  Also, our Monte Carlo estimates are highly dependant on parameters such as firm value if firm value is well above debt value and the volatility of the firm is low, the chance of default is really low.
